Reply to Reviewer #1

### 2022-02-06 Writing/JournalSubmission/ML_for_VRA.Rmd
Correct the structure of CF_for_VRA folder

---
title: "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation"
author: Shunkei Kakimoto^[Corresponding author, Department of Agricultural Economics, University of Nebraska-Lincoln 102 Filley Hall 1625 Arbor Drive Lincoln, NE 68583, USA, E-mail address; skakimoto3@hunskers.unl.edu], Taro Mieno^[Department of Agricultural Economics, University of Nebraska-Lincoln, Lincoln, NE 68583, USA], Takashi S. T. Tanaka^[Artificial Intelligence Advanced Research Center, Faculty of Applied Biological Sciences, Gifu University, Gifu 501-1193, Japan], and David S. Bullock^[Department of Agricultural and Consumer Economics, University of Illinois, Urbana, IL 61801, USA]
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: yes
    global_numbering: true
    # reference_docx: word_template.docx
    reference_docx: word_template_format.docx
    # pandoc_args: ["-Fpandoc-crossref"]
bibliography: ML_VRA.bib
csl: computers-and-electronics-in-agriculture.csl
eqnPrefix: 
      - "Eq"
abstract: "Estimating site-specific crop yield response to changes in input (e.g., seed, fertilizer) management is a critical step in making economically optimal site-specific input recommendations. Past studies have attempted to estimate yield response functions using various Machine Learning (ML) methods, including the Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN) methods. This study proposes use of the Causal Forest (CF) model, which is one of the emerging ML methods that comprise \"Causal Machine Learning.\" Unlike previous prediction-oriented ML methods, CF focuses strictly on estimating heterogeneous treatment effects of inputs, rather than predicting yield. We report results of using Monte Carlo simulations assuming various production scenarios to test the effectiveness of CF in estimating site-specific economically optimal nitrogen rates (EONRs), comparing CF with the yield-prediction-oriented ML methods RF, BRF, and CNN. CF's estimations of site-specific EONRs were superior under all scenarios considered. Furthermore, we also show that the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions."  
---

@@

```{r, cache = TRUE}
# === packages ===#
library(sf)
library(png)
library(data.table)
library(grf)
library(RColorBrewer)
library(patchwork)
library(plotly)
library(magrittr)
library(ggplot2)
library(viridis)
library(tmap)
library(tidyverse)
library(ggthemes)
library(mgcv)
library(ggpubr)
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(raster)
library(bookdown)
```

@@

# Keywords: {-}

@@

CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a]. Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf. Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) and topographical $\textit{slope}$ as variables to explain the heterogeneity of the impact of the treatment impact. 
In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example.

```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An Illustrative Example of Causal Tree"}
knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/ctree_ex.png"))
```

The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$. The observations with $\textit{ecs}$ greater than or equal to $25$ move to the left node, while those with $\textit{ecs}$ less than $25$ move to the right. For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample. The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha. This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas. Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects. The estimated CF model does not predict yield level at any site $i$ in the field, but rather estimates site-specific EOIRs by estimating treatment effects. Since CF is designed to estimate the causal effect of an input directly, it may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction.

@@

```{r field-map, fig.width=4, fig.height=3, fig.cap = "Division of Field: plots, subplots and cells"}
knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/field_devision.png"))

```

@@

```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics"}
# field_alpha + field_beta + field_ymax
grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
```

@@

```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Spatial Distribution of True Optimal N Rate"}
vis_optN_cell
```

@@

In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs. Then, the five trial design rates were

@@

In each round, a Latin square design was followed to assign each plot one of the five N rates so established. Figure \@ref(fig:fig-nExp) shows an example of a trial design.

```{r fig-nExp, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of Experimental Design of N"}
field_Ndesign
```

Under this design, the N rate was orthogonal to the error term. This is important because if they were correlated, bias in the estimation of the impact of nitrogen on yield would be introduced for all of the ML methods. Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently. Note that the violation of this condition leads to biased estimation for not just CF and the other ML methods, as well.

@@

A cell-level data set for the whole field, $\{(y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}, j \in \{1,2,...,36\}\}$ was generated. For a generic cell $(i,j)$, yield $y^{i,j}$ was generated through Eq. \@ref(eq:eqn3), applying parameter values $\mathbf{c^{i,j}}=(\alpha^{i,j}, \beta^{i,j}, ymax^{i,j})$, the disturbance term level $\varepsilon^{i,j}$, and the cell's assigned experimental N rate, $N^{i,j}$ (Figure \@ref(fig:field-yield-cell)).

```{r field-yield-cell, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Cell resolution"}
vis_yield_cell
```

These were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation. The subplot data were therefore

@@

```{r field-yield-subplot, fig.width=3, fig.height=4, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Subplot resolution"}
vis_yield_subplot
```

@@

Table \@ref(tab:table-optN-subplot-wide) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the $1000$ simulations; it makes immediately clear that CF-base considerably outperformed the other ML methods, and that the profits based on CF-base's EONR estimates were the closest to the true maximum profits. BRF performed considerably better predicting EONR than did RF.

Interestingly, CNN completely failed in its estimations of site-specific EONRs. This happened because the site-specific yield response functions identified by CNN were linear, and all with the same slope. Therefore, CNN failed to capture a declining marginal product of N. The constant marginal product caused the estimated EONR to take on either the lowest or highest experimental N application rate. To examine whether this problem is product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling. 
This architecture also estimated that yield and N rates were perfectly linearly related, and also estimated site-specific EONR poorly. Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs. In some cases, CNN predicted yield well; but in all cases it predicting EONR poorly.

@@

```{r dist-optN, fig.width=6, fig.height=7, fig.cap = "Distributions of RMSE of EONR Estimation over Simulations"}
plot_dis_optN
```

```{r dist-piLoss, fig.width=6, fig.height=7, fig.cap = "Distributions of Profit Deficit over Simulations"}
piLoss_density
```

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the $1000$ simulations rounds. The figure shows that the estimated treatment effects did not exhibit significant bias, with the points clustered around the red 1-to-1 line. However, they differ substantially in the accuracy of their treatment effect estimations. Points are clustered much more tightly about the 1-to-1 line much for CF-base than RF and BRF. That is, CF-base estimates treatment effects much more efficiently than do the RF and BRF methods, which focus on yield prediction rather than treatment effect estimation.

```{r plot-tre, fig.width=7, fig.height=5, fig.cap = "True Treatment Effects vs Estimated Treatment Effects (Scenario: aabbyytt)"}
figure_te
```

## Yield Prediction and EONR Estimation
For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red line shows the best-fit line describing the relationship between them. 
For all the models the regression line was almost flat, showing little if any correlation between the two measures. In other words, the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions.

```{r plot-y-optN, fig.width=7, fig.height=5, fig.cap = "The Relationship in the Performance between EONR Estimation and Yield Prediction by ML Methods and Modeling Scenarios"}
fig_y_optN
```

@@

# Acknowledgement

@@

>>>>

---
title: "Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation"
author: Shunkei Kakimoto^[Corresponding author, Department of Agricultural Economics, University of Nebraska-Lincoln 102 Filley Hall 1625 Arbor Drive Lincoln, NE 68583, USA, E-mail address; skakimoto3@hunskers.unl.edu], Taro Mieno^[Department of Agricultural Economics, University of Nebraska-Lincoln, Lincoln, NE 68583, USA], Takashi S. T. Tanaka^[Artificial Intelligence Advanced Research Center, Faculty of Applied Biological Sciences, Gifu University, Gifu 501-1193, Japan], and David S. Bullock^[Department of Agricultural and Consumer Economics, University of Illinois, Urbana, IL 61801, USA]
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: yes
    global_numbering: true
    reference_docx: word_template.docx
    # reference_docx: word_template_format.docx
    # pandoc_args: ["-Fpandoc-crossref"]
bibliography: ML_VRA.bib
csl: computers-and-electronics-in-agriculture.csl
eqnPrefix: 
      - "Eq"
abstract: "Estimating site-specific crop yield response to changes in input (e.g., seed, fertilizer) management is a critical step in making economically optimal site-specific input recommendations. Past studies have attempted to estimate yield response functions using various Machine Learning (ML) methods, including the Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN) methods. This study proposes use of the Causal Forest (CF) model, which is one of the emerging ML methods that comprise \"Causal Machine Learning.\" Unlike previous prediction-oriented ML methods, CF focuses strictly on estimating heterogeneous treatment effects of inputs, rather than predicting yield. We report results of using Monte Carlo simulations assuming various production scenarios to test the effectiveness of CF in estimating site-specific economically optimal nitrogen rates (EONRs), comparing CF with the yield-prediction-oriented ML methods RF, BRF, and CNN. CF's estimations of site-specific EONRs were superior under all scenarios considered. Furthermore, we also show that the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions."  
---

@@

```{r, cache = TRUE}
# === packages ===#
library(sf)
library(data.table)
library(grf)
library(RColorBrewer)
library(patchwork)
library(plotly)
library(magrittr)
library(ggplot2)
library(viridis)
library(tmap)
library(tidyverse)
library(ggthemes)
library(mgcv)
library(ggpubr)
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(raster)
library(bookdown)
```

@@

# Keywords:

@@

CF was developed specifically for identifying heterogeneous treatment effects [@athey2016recursive; @Wager2018a]. Like RF, CF works by building an ensemble of trees, called *causal trees* (CT), by recursively partitioning covariate space into two leaves, where each leaf estimates conditional average treatment effects as the mean differences between the dependent variable (here, yield) of the treated and control observations that belong to the leaf. Figure \@ref(fig:ct-ex) shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) and topographical $\textit{slope}$ as variables to explain the heterogeneity of the impact of the treatment impact. 
In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example. The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$. The observations with $\textit{ecs}$ greater than or equal to $25$ move to the left node, while those with $\textit{ecs}$ less than $25$ move to the right. For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample. The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha. This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas. Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects. The estimated CF model does not predict yield level at any site $i$ in the field, but rather estimates site-specific EOIRs by estimating treatment effects. Since CF is designed to estimate the causal effect of an input directly, it may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction.

@@

@@

@@

@@

In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs. Then, the five trial design rates were \

@@

In each round, a Latin square design was followed to assign each plot one of the five N rates so established. Figure \@ref(fig:fig-nExp) shows an example of a trial design. Under this design, the N rate was orthogonal to the error term. This is important because if they were correlated, bias in the estimation of the impact of nitrogen on yield would be introduced for all of the ML methods. Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently. Note that the violation of this condition leads to biased estimation for not just CF and the other ML methods, as well.

<!-- Resulting mean yield of $1.1250\times10^4 \text{ } kg/ha$. The magnitude of the error term is set to vary yields by approximately $1245 \text{ }(kg/ha)$ on average from deterministic yields. 
 -->

@@

A cell-level data set for the whole field, $\{(y^{i,j}, N_{opt}^{i,j}, N^{i,j}, \mathbf{c}^{i,j}): i \in \{1,2,...,1536\}, j \in \{1,2,...,36\}\}$ was generated. For a generic cell $(i,j)$, yield $y^{i,j}$ was generated through Eq. \@ref(eq:eqn3), applying parameter values $\mathbf{c^{i,j}}=(\alpha^{i,j}, \beta^{i,j}, ymax^{i,j})$, the disturbance term level $\varepsilon^{i,j}$, and the cell's assigned experimental N rate, $N^{i,j}$ (Figure \@ref(fig:field-yield-cell)). These were aggregated up to the subplot level by taking the mean of the cell-level values inside each subplot, which were the unit of observation. The subplot data were therefore

@@

@@

Table \@ref(tab:table-optN-subplot-wide) shows the mean RMSE of the EONR estimation and $\hat{\pi}_{def}$ over the $1000$ simulations; it makes immediately clear that CF-base considerably outperformed the other ML methods, and that the profits based on CF-base's EONR estimates were the closest to the true maximum profits. BRF performed considerably better predicting EONR than did RF. Interestingly, CNN completely failed in its estimations of site-specific EONRs. This happened because the site-specific yield response functions identified by CNN were linear, and all with the same slope. Therefore, CNN failed to capture a declining marginal product of N. The constant marginal product caused the estimated EONR to take on either the lowest or highest experimental N application rate. To examine whether this problem is product solely of the specific choice of CNN architecture, we also tested another CNN model, which was analogous to CNN-ST proposed by @barbosa2020modeling. 
This architecture also estimated that yield and N rates were perfectly linearly related, and also estimated site-specific EONR poorly. Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs. In some cases, CNN predicted yield well; but in all cases it predicting EONR poorly.

@@

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the $1000$ simulations rounds. <!-- To illustrate differences between the ML methods, -->The figure shows that the estimated treatment effects did not exhibit significant bias, with the points clustered around the red 1-to-1 line. However, they differ substantially in the accuracy of their treatment effect estimations. Points are clustered much more tightly about the 1-to-1 line much for CF-base than RF and BRF. That is, CF-base estimates treatment effects much more efficiently than do the RF and BRF methods, which focus on yield prediction rather than treatment effect estimation.

## Yield Prediction and EONR Estimation

For RF, BRF and CNN, Figure \@ref(fig:plot-y-optN) plots the RMSE values of EONR estimation against the RMSE values of yield prediction, and the red line shows the regression line describing the relationship between them. 
For all the models the regression line was almost flat, showing little if any correlation between the two measures. In other words, the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions. 
<!-- For all the models the figure shows little if any correlation between the two measures. In other words, the quality of a model's yield predictions provides little if any information about the quality of its EONR predictions.  -->

@@

# Funding

@@

# Tables

# Figures

<br>
<!-- 
1. add the distribution of the resutls
2. add the distribution of each parameters -->
<!-- when you mention a figure, use "Figure \@ref(fig:fig-1)"  -->

```{r ct-ex, fig.width=7, fig.height=10, fig.align="center", fig.cap = "An Illustrative Example of Causal Tree"}
knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/ctree_ex.pdf"))
```

```{r field-map, fig.width=7, fig.height=10, fig.cap = "Division of Field: plots, subplots and cells"}
knitr::include_graphics(here("GitControlled/Writing/JournalSubmission/field_devision.pdf"))
```

```{r fig-parameters, fig.width=9, fig.height=10, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics"}
# field_alpha + field_beta + field_ymax
grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
```

```{r fig-optN,  fig.cap = "An Illustrative Example of a Spatial Distribution of True Optimal N Rate"}
vis_optN_cell
```

<!-- \newpage -->

```{r fig-nExp, fig.width=7, fig.height=9, fig.cap = "An Illustrative Example of Experimental Design of N"}
field_Ndesign
```

```{r field-yield-cell, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Cell resolution"}
vis_yield_cell
```

```{r field-yield-subplot, fig.cap = "An Illustrative Example of a Yield Distribution Map at the Subplot resolution"}
vis_yield_subplot
```

```{r dist-optN, fig.width=7, fig.height=8, fig.cap = "Distributions of RMSE of EONR Estimation over Simulations"}
plot_dis_optN
```

```{r dist-piLoss, fig.width=7, fig.height=8, fig.cap = "Distributions of Profit Deficit over Simulations"}
piLoss_density
```

```{r plot-tre, fig.width=8, fig.height=9, fig.cap = "True Treatment Effects vs Estimated Treatment Effects (Scenario: aabbyytt)"}
figure_te
```

```{r plot-y-optN, fig.width=8, fig.height=9, fig.cap = "The Relationship in the Performance between EONR Estimation and Yield Prediction by ML Methods and Modeling Scenarios"}
fig_y_optN
```

### 2022-02-06 Writing/Re_JournalSubmission/replies_rev_1.rmd
Correct the structure of CF_for_VRA folder

---
title: "Reply to Reviewer #1"
author: 
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

@@

**Materials and Method to just Method: Monte Carlo Simulations?**

The core objective is to test the CF against existing ML methods. To this core objective, ML simulations are our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood by the reader of this journal. Since, this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place this inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Instead of this, we believe that it is beneficial to first give the readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted.

We talk about identifying site-specific economically optimal input rates in three different places. Therefore, I understand why you feel there are redundancies. However, each of them serves distinctive purposes and we would like to keep the current structure if that is acceptable to you.

Section 2.1: bluh bluh
Section 3.: true optimal N
Section 3.: estiamted optimal N

@@

**3. The description of materials and methods section is redundant, please move some unimportant details description to supplementary materials.**

<span style="color:blue">  
We first apologogize that misleading section and subsection titles may have caused confusions about your perceived structural redundancy of this article.

We wrote the initial manuscript with avoiding redundancy in mind and we beleived that we did not have any redundancy in our paper. Therefore, we struggled tremendously to see where the redundancies are. We would really appreciate it if you could specify where you see redundancies and why so that we can address prorperly.

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our manuscript is appropriate. Therefore, we had very hard time telling which is unnecessary and not. We would really appreciate it if you could specify which parts are not critical.

@@

+ It is degree. <!-- The slope is obtained by dividing the rise over run. If slope is 0.005857921, it means that the field is raised by 0.005857921 m for every 1m you move horizontally.  -->
+ I added the the unit of EC (dS/m) additionally, since another reviewer pointed out the units of EC

@@

+ I added the explanation for those numbers in the footnote. 
</span>

@@

+ I numbered only referenced equations. Should I number all the equations?
</span>

@@

+ I changed this sentence "For each simulated field, we generated a training data set and a validation data set."

+ The modified version is "After generating one thousand synthetic fields, we repeated to evaluate each of the ML methods by one thousand times. In an individual simulation round, one of the fields was used as a training data set. As a validation data set, a different field from a training data set in that simulation round was used".
</span>

**8. I can’t open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox). Please upload the code to the public research data repositories (Zenodo, Mendeley Data, figshare, Harvard Dataverse, etc.), not GitHub. Please generate a separate DOI for your code and cite it.**
<span style="color:blue">

@@

+ I converted to those units to meter (m)
  + plot size: 60-ft × 240-ft -> 18.288-m × 73.152-m
  + subplot size: 60-ft × 60-ft -> 18.288-m × 18.288-m
  + plot size: 10-ft × 10-ft -> 3.048-m × 3.048-m
</span>

@@

+ I added the number of rows and columns of plots, subplots and cells in Figure 2. 
</span>

@@

+ Current name:
  + 3.2 OFPE Experiments and Estimating Site-specific Optimal N Rates
    + 3.2.1 RF, BRF, and CNN
    + 3.2.2 CF

+ The title of section 3.2.1: Site-specific EONR estimation by RF, BRF, and CNN
+ The title of section 3.2.1: Site-specific EONR estimation by CF

+ Or, we could change the title of section 3.2 (e.g., Machine Learning Algorithm to Estimate Site-specific EONR) and use the same title for section 3.2.1 and 3.2.2
</span>

@@

+ Current name:
  + 4.1 EONR Estimation
  + 4.2 Yield Prediction and EONR Estimation

+ The title of section 4.2 could be changed to "The relationship between the performance of yield prediction and EONR estimation" (?)
</span>

@@

+ I need to add the explanation for it in section 4.1 EONR estimation.  
</span>

>>>>

---
title: "Reply to Reviewer #1"
author: Shunkei Kakimoto
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

@@

@@

**3. The description of materials and methods section is redundant, please move some unimportant details description to supplementary materials.**
<span style="color:blue">

@@

+ I provided the unit in the text. It is degree.

@@

+ I added the explanation for those numbers as a footnote in the figure. 
</span>

@@

+ I numbered all the formulas. 
</span>

@@

+ I modified this sentence "For each simulated field, we generated a training data set and a validation data set." For each simulation round, one of the fields was used as a training data set, and another field that is different from the one used as a training data set in that round was used as a validation data set.

**8. I can’t open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox). Please upload the code to the public research data repositories (Zenodo, Mendeley Data, figshare, Harvard Dataverse, etc.), not GitHub. Please generate a separate DOI for your code and cite it.**
<span style="color:blue">  
+ I uploaded to the simulation codes and the data on Mendeley Data. The link is suggested on section 3: Materials and Methods.

@@

+ I converted to those units to meter (m)

@@

+ I updated Figure 2. The number of rows and columns of plots, subplots, and cells schematics are indicated each map in Figure 2.
</span>

@@

+ I changed the title of section 3.2 to "Training Models and Estimating Site-specific EONRs". Further, I revised the title of sections 3.2.1 and 3.2.2 to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively. 
</span>

@@

+ I changed the title of section 4.2 to "The relationships between yield prediction performance and EONR prediction performance". 
</span>

@@

+ As explained in section 4.1, CNN completely failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1). Therefore, I do not think that visualizing the CNN results provide any meaningful implications to understand its performance of EONR estimation performance.
+ I added the explanation for not showing CNN results in Figures 8,9, and 10. ("CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively")
